\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-06-12 learning.tex
.

>>>>

\begin{example}
    For the~\exref{vdp}, for each cell $C$, regression
    analysis is performed on the respective set of trajectory segments $D(C)$, and
    compute a set of affine relations $R_{C,C'}(\x,\x')$ between $\x
    \in C$ and $\x' \in C'$ s.t., $\text{edge} (C,C') \in
    \scr{H}(0.1)$. Annotate each edge in the graph $\scr{H}(0.1)$ with
    the respective relation.

    \figref{vdp-abs-paths} shows the cells and the trajectory segments, which
    are part of the data sets constructed using the $1$-relational
    modeling. Against each cell, its unique identifier (integer
    co-ordinate) is mentioned.  Finally, \figref{vdp-graph} and
    \tabref{vdp-pwa} show the enriched graph $G^R$ with its transition
    relations. Note that self loops result when an observed trajectory
    segment has its $start$ and $end$ states in the same cell.
\end{example}

### 2017-06-12 scam.tex
.

\begin{example}
\inclfig[width=0.90\linewidth]{vdp_disc_map.pdf}{Cells and
trajectory segments used by $1$-relational modeling.}{vdp-abs-paths}

Going back to the example~\exref{vdp}, $ScatterAndSimulate$ is able to
    find several abstract trajectories as shown
    in~\figref{vdp-abs-paths}. However, typically, the refinement by
    increasing the quantization precision requires $4$ refinement
    iterations and finally finds a concrete counter-example for
    $\epsilon=0.125$.
\end{example}

>>>>

\begin{example}
\inclfig[width=0.90\linewidth]{vdp_disc_map.pdf}{
Abstract trajectories discovered by $ScatterAndSimulate$. Each
    rectangle denotes a cell which is uniquely identified  by the
    tuple against it.
%Cells and trajectory segments used by $1$-relational modeling.
}{vdp-abs-paths}

Going back to the~\exref{vdp}, $ScatterAndSimulate$ is able to
    find several abstract trajectories as shown
    in~\figref{vdp-abs-paths}. However, typically, the refinement by
    increasing the quantization precision requires $4$ refinement
    iterations and finally finds a concrete counter-example for
    $\epsilon=0.125$.
\end{example}
